### 2023-05-26 definitions.tex
sections

A WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ is {\em effective} if there exists a pair of Turing machines
($M_\rightarrow$, $M_\leq$) operating on $\N \times \N$ such that
$ M_\rightarrow$ computes the transition relation “$\rightarrow$” and 
$M_\leq$ the ordering relation “$\leq$”.

We say that $\mathscr{S}$ is {\em post-effective} if it is effective, and if there
exists an additional Turing machine that computes $|\post(x)| \in \N \cup \{\infty\}$ 
on input $x$, with $x \in X_i $. 
Such a Turing machine, in combination with $M_\rightarrow$, allows computing
$\post(x)$ whenever the latter is finite.

We will use the following property: if $\mathscr{S}$ is a WSTS with strong compatibility and $U \subseteq S$ is upward-closed, then $\pred(U )$, $\pred^k(U )$ with $k\geq0$, and $\pred^*(U )$ are all upward-closed \cite{DBLP:journals/tcs/FinkelS01}.
%\alain{étrange ces deux propositions, l'une suffirait}

\iffalse
Proof. Assume $s \in \pred (I )$. Then $s \rightarrow t$ for some $t \in I $. If now $s' \geq s$ then strong upward-compatibility entails that $s' \rightarrow t'$ for some $t' \geq t$. Then $t' \in I$ and $s' \in \pred(I )$.
\fi
%

@@

\begin{definition}\cite{DBLP:journals/tcs/FinkelS01,DBLP:journals/iandc/AbdullaCJT00}
A WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ has {\em effective pred-basis} if there exists an algorithm accepting
any state $s \in S$ and returning $pb(s)$, a finite basis of $\uparrow \pred(\uparrow s)$.
\end{definition}

@@

We say that $\mathscr{S}$
is {\em ideally effective} \cite{BFM-ic17} if (1) the function mapping the encoding of a configuration $s$
to the encoding of the ideal $\downarrow s$ is computable; (2) inclusion of ideals is decidable; (3) the downward closure $\downarrow \post(I)$ expressed as a finite union of ideals is computable from the ideal $I$.
%
\iffalse
\alain{pas ici}
\begin{definition}{\cite{BFM-ic17}} 
A class $C$ of WSTS is {\em ideally effective} if
\begin{itemize}
\item the function mapping the encoding of a configuration $s$ of a WSTS
to the encoding of the ideal $\downarrow s$ is computable;
\item inclusion of ideals is decidable;
\item the downward closure $\downarrow \post(I)$ expressed as a finite union of ideals is computable from the ideal $I$.
\end{itemize}
\end{definition}
%
\fi
%
%
With the ideally effective hypothese, we obtain the decidability of coverability for a class of ordered transition systems larger than WSTS.

>>>>

{\bf On effectivity}
A WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ is {\em effective} if there exists a pair of algorithms
($M_\rightarrow$, $M_\leq$) operating on $\N \times \N$ such that
$ M_\rightarrow$ computes the transition relation “$\rightarrow$” and 
$M_\leq$ the ordering relation “$\leq$”.

A WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ has {\em effective pred-basis} \cite{DBLP:journals/tcs/FinkelS01,DBLP:journals/iandc/AbdullaCJT00} if there exists an algorithm accepting
any state $s \in S$ and returning $pb(s)$, a finite basis of $\uparrow \pred(\uparrow s)$.

%\alain{étrange ces deux propositions, l'une suffirait}
%%%%%%%%%%%%%%%%%
\iffalse
%%%%%%%%%%%%%
Proof. Assume $s \in \pred (I )$. Then $s \rightarrow t$ for some $t \in I $. If now $s' \geq s$ then strong upward-compatibility entails that $s' \rightarrow t'$ for some $t' \geq t$. Then $t' \in I$ and $s' \in \pred(I )$.
%%%%%%%%%%%
\fi
%%%%%%%%%%

@@

We will use the following property: if $\mathscr{S}$ is a WSTS with strong compatibility and $U \subseteq S$ is upward-closed, then $\pred(U )$, $\pred^k(U )$ with $k\geq0$, and $\pred^*(U )$ are all upward-closed \cite{DBLP:journals/tcs/FinkelS01}.

@@

We say that $\mathscr{S}$
is {\em ideally effective} \cite{BFM-ic17} if (1) the function mapping the encoding of a configuration $s$
to the encoding of the ideal $\downarrow s$ is computable; (2) inclusion of ideals is decidable; (3) the downward closure $\downarrow \post(I)$ expressed as a finite union of ideals is computable from the ideal $I$.
%
\iffalse
%%%%%%%%%

%%%%%%%%%

\alain{pas ici}
\begin{definition}{\cite{BFM-ic17}} 
A class $C$ of WSTS is {\em ideally effective} if
\begin{itemize}
\item the function mapping the encoding of a configuration $s$ of a WSTS
to the encoding of the ideal $\downarrow s$ is computable;
\item inclusion of ideals is decidable;
\item the downward closure $\downarrow \post(I)$ expressed as a finite union of ideals is computable from the ideal $I$.
\end{itemize}
\end{definition}
%
\fi
%
%
With the ideally effective hypothese, we obtain the decidability of coverability for a class of ordered transition systems larger than WSTS.

### 2023-05-26 resilience-safe-up.tex
sections

@@

% \mathieu{I'm using the notion of ideally effective-ness for WBTS here}
%
Let us recall that the \emph{completion}  \cite{BFM-ic17} of a WSTS $\mathscr{S}=(S,\rightarrow, \leq)$ is the associated ordered transition system $\hat{\mathscr{S}}=(Ideals(S),\rightarrow, \subseteq)$ where states of $\hat{\mathscr{S}}$ are ideals of $S$ and $I \rightarrow J$ if $J$ belongs to the finite ideal decomposition of $\downarrow \post_{\mathscr{S}}(I)$. The completion is always finitely branching but it is not necessarly WSTS since $\subseteq$ is not necessarly a wqo. $\hat{\mathscr{S}}$ is WSTS iff $\mathscr{S}=(S,\rightarrow, \leq)$ is $\omega^2$-WSTS (intuitively speaking, $(S,\leq)$ must not contain the Rado set). 
A WSTS $\mathscr{S}=(S,\rightarrow,\leq)$ is {\em completion-post-effective} if
it is post-effective, and there exists a Turing Machine $M_\downarrow$ that computes, on input $s \in S$, % some $\hat(e) \in \hat( ... )$ such that
 $\downarrow s$, and some Turing Machine $M_{\uparrow^C}$ that computes, on input
 $\{s_1, s_2, \ldots, s_m\} \in S^m$, 
 the ideal decomposition of $S \setminus \uparrow \{ s_1, s_2, \ldots, s_m\}$.
Coverability is shown decidable  [Theorem 44] in \cite{BFM-ic17} for completion-post-effective $\omega^2$-WSTS.

>>>>

We say that $\mathscr{S}$ is {\em post-effective} if it is effective, and if there
exists an algorithm that computes $|\post(x)| \in \N \cup \{\infty\}$ 
on input $x$, with $x \in X_i $. 
%Such a Turing machine, in combination with $M_\rightarrow$, allows computing
%$\post(x)$ whenever the latter is finite.

@@

% \mathieu{I'm using the notion of ideally effective-ness for WBTS here}
%
Let us recall that the \emph{completion}  \cite{BFM-ic17} of a WSTS $\mathscr{S}=(S,\rightarrow, \leq)$ is the associated ordered transition system $\hat{\mathscr{S}}=(Ideals(S),\rightarrow, \subseteq)$ where states of $\hat{\mathscr{S}}$ are ideals of $S$ and $I \rightarrow J$ if $J$ belongs to the finite ideal decomposition of $\downarrow \post_{\mathscr{S}}(I)$. The completion is always finitely branching but it is not necessarly WSTS since $\subseteq$ is not necessarly a wqo. $\hat{\mathscr{S}}$ is WSTS iff $\mathscr{S}=(S,\rightarrow, \leq)$ is $\omega^2$-WSTS (intuitively speaking, $(S,\leq)$ must not contain the Rado set). 
A WSTS $\mathscr{S}=(S,\rightarrow,\leq)$ is {\em completion-post-effective} if
it is post-effective, and there exists a Turing Machine $M_\downarrow$ that computes, on input $s \in S$, % some $\hat(e) \in \hat( ... )$ such that
 $\downarrow s$, and some Turing Machine $M_{\uparrow^C}$ that computes, on input
 $\{s_1, s_2, \ldots, s_m\} \in S^m$, 
 the ideal decomposition of $S \setminus \uparrow \{ s_1, s_2, \ldots, s_m\}$.
Coverability is shown decidable  [Theorem 44] in \cite{BFM-ic17} for completion-post-effective $\omega^2$-WSTS (we don't need the pred-basis hypothesis).

### 2023-05-26 state-resilience.tex
sections

\begin{proposition}[Adjusting Theorem~5.5 from \cite{peterson1981petri}]\label{liveness reset}
The  zero reachability problem can be reduced to the $t$-liveness problem in Reset VASS.
\end{proposition}

>>>>

Adjusting Theorem~5.5 from \cite{peterson1981petri}:

\begin{proposition}\label{liveness reset}
The  zero reachability problem can be reduced to the $t$-liveness problem in Reset VASS.
\end{proposition}
